Home Nighttime Cough Monitoring

### 2025-02-13 Lilah Melzer/cough_monitor_analysis.qmd
Update cough_monitor_analysis.qmd

agg_counts <- left_join(agg_counts, cfqr_parent_6_13)
agg_counts <- left_join(agg_counts, cfqr_children_6_11)
agg_counts <- left_join(agg_counts, cfqr_teens_adults)

@@

## Correlation between baseline surveys and coughs

```{r}
```

>>>>

agg_counts <- full_join(agg_counts, cfqr_parent_6_13)
agg_counts <- full_join(agg_counts, cfqr_children_6_11)
agg_counts <- full_join(agg_counts, cfqr_teens_adults)

@@
